\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}

\begin{center}
\textbf{Classical Stokes Theorems}
\end{center}

\paragraph{Def:} A \textit{vector field} on $\mathbb{R}^n$ is a vector-valued function $F: \mathbb{R}^n \to \mathbb{R}^m$. If $x_1,\dots,x_n$ are coordinates for $\mathbb{R}^n$, then the vector field $F$ will be described by $m$ real-valued functions $f_k: \mathbb{R}^n \to \mathbb{R}$ as follows
$$ F(x_1,\dots,x_n) = 
\begin{pmatrix}
f_1(x_1,\dots,x_n)\\
\vdots\\
f_m(x_1,\dots,x_n)
\end{pmatrix}$$

\paragraph{Def:} A vector field is \textit{continuous} if each real-valued function $f_k$ is continuous.

\paragraph{Def:} A vector field is \textit{differentiable} if each real-valued function $f_k$ is differentiable.

\paragraph{Note:} A vector field is essentially a function that you plug a vector in and get a vector out. There is no connection to the abstract algebra idea of a field. (Stupid physicists, always ruining perfectly good math)

\paragraph{Def:} A \textit{differentiable manifold} $M$ of dimension $k$ in $\mathbb{R}^n$ is a set of points in $\mathbb{R}^n$ such that for any point $p \in M$, there is a small open neighborhood $U$ of $p$, a vector-valued differentiable function $F:\mathbb{R}^k \to \mathbb{R}^n$ and an open set $V$ in $\mathbb{R}^k$ with
\begin{enumerate}
\item $F(V) = U \cap M$
\item The Jacobian of $F$ has rank $k$ at every point in $V$
\end{enumerate}
The function $F$ is called the \textit{parametrization} of the manifold.

\paragraph{Note:} The reason why the Jacobian needs to have rank equal to the dimension of the manifold is so the Jacobian will have a $k\times k $ minor.

\paragraph{Examples:} A circle is a 1-dimensional manifold in 2-space. A cone is a 2-dimensional manifold in 3-space.

\paragraph{Def:} The \textit{closure} of $M$, denoted $\bar{M}$, is the set of all points $x$ in $\mathbb{R}^n$ such that there is a sequence of points $\{x_n\}$ in the manifold $M$ with
$$\lim_{n \to \infty} x_n = x$$
The \textit{boundary} of $M$, denoted $\partial M$, is:
$$ \partial M = \bar{M} - M$$

\paragraph{Note:} The boundary of an $n$-dimensional manifold is usually either empty or is a $(n-1)$-dimensional manifold.

\end{document}